The Chemistry Development Kit (CDK). 3. Atom typing, Rendering, Molecular Formula, and Substructure Searching

### 2016-08-28 article.tex
Revert "Gilleain thanked for the offer and cannot contribute to the paper (personal communication)"
This reverts commit c24afea8ae9f4f97ef5d66a439379b6af9569356.
Details Gilleain (happy to have on board) and a few other minor updates (still hoping to get a reply from Miquel)

\author[
   addressref={um},                   % id's of addresses, e.g. {aff1,aff2}
   %corref={aff1},                       % id of corresponding address, if any
   %noteref={n1},                        % id's of article notes, if any
   email={egon.willighagen@maastrichtuniversity.nl}   % email address
]{\inits{ELW}\fnm{Egon L} \snm{Willighagen}}
\author[
   addressref={aff2},
   email={john@nextmovesoftware.com}
]{\inits{JWM}\fnm{John W} \snm{May}}
\author[
   addressref={uppsala},
   email={jonathan.alvarsson@farmbio.uu.se}
]{\inits{JA}\fnm{Jonathan} \snm{Alvarsson}}
\author[
   addressref={uppsala},
   email={berg.arvid@gmail.com}
]{\inits{AB}\fnm{Arvid} \snm{Berg}}
\author[
   addressref={jena},
   email={kai.duehrkop@uni-jena.de}
]{\inits{KD}\fnm{Kai} \snm{Dührkop}}
\author[
   addressref={idea},
   email={jeliazkova.nina@gmail.com}
]{\inits{NJ}\fnm{Nina} \snm{Jeliazkova}}
\author[
   addressref={leicester},
   email={shk12@le.ac.uk}
]{\inits{SK}\fnm{Stefan} \snm{Kuhn}}
\author[
   addressref={wi_mit},
   email={pluskal@wi.mit.edu}
]{\inits{TP}\fnm{Tomáš}~\snm{Pluskal}}
\author[
   addressref={???},
   email={miguelrojasch@googlemail.com}
]{\inits{MRJ}\fnm{Miguel}~\snm{Rojas-Cherto}}
\author[
   addressref={uppsala},
   email={ola.spjuth@farmbio.uu.se}
]{\inits{OS}\fnm{Ola} \snm{Spjuth}}
\author[
   addressref={um},
   email={chris.evelo@maastrichtuniversity.nl}
]{\inits{CTE}\fnm{Chris T} \snm{Evelo}}
\author[
   addressref={nih},
   email={guhar@mail.nih.gov}
]{\inits{RG}\fnm{Rajarshi} \snm{Guha}}
\author[
   addressref={ebi},
   email={steinbeck@ebi.ac.uk}
]{\inits{CS}\fnm{Christoph}~\snm{Steinbeck}}

\address[id=um]{
  \orgname{Dept of Bioinformatics - BiGCaT, NUTRIM, Maastricht University}, % university, etc
  %\street{Waterloo Road},                     %
  \postcode{NL-6200 MD},
  \city{Maastricht},                              % city
  \cny{The Netherlands}                                    % country
}
\address[id=aff2]{
  \orgname{??},
  %\street{D\"{u}sternbrooker Weg 20},
  %\postcode{24105},
  %\city{Kiel},
  \cny{UK}
}
\address[id=uppsala]{
  \orgname{Department of Pharmaceutical Biosciences, Uppsala University},
  %\street{D\"{u}sternbrooker Weg 20},
  \postcode{751 24},
  \city{Uppsala},
  \cny{Sweden}
}
\address[id=jena]{
  \orgname{Chair for Bioinformatics, Friedrich Schiller University},
  %\street{},
  \postcode{07743},
  \city{Jena},
  \cny{Germany}
}
\address[id=idea]{
  \orgname{Ideaconsult Ltd},
  \street{A. Kanchev 4},
  \postcode{1000},
  \city{Sofia},
  \cny{Bulgaria}
}
\address[id=wi_mit]{
  \orgname{Whitehead Institute for Biomedical Research}, 
  \street{9 Cambridge Center},
  \postcode{MA 02142},
  \city{Cambridge},
  \cny{USA}
}
\address[id=nih]{
  \orgname{National Center for Advancing Translational Science},
  \street{9800 Medical Center Drive},
  \postcode{MD 20878},
  \city{Rockville},
  \cny{USA}
}
\address[id=ebi]{
  \orgname{Chemoinformatics and Metabolism team, European Bioinformatics Institute},
  %\street{A. Kanchev 4},
  %\postcode{1000},
  \city{Hinxton},
  \cny{UK}
}
\address[id=leicester]{
  \orgname{Department of Informatics, University of Leicester},
  %\street{},
  %\postcode{LE1 7RH},
  \city{Leicester},
  \cny{UK}
}

>>>>

\author[
   addressref={um},                   % id's of addresses, e.g. {aff1,aff2}
   %corref={aff1},                       % id of corresponding address, if any
   %noteref={n1},                        % id's of article notes, if any
   email={egon.willighagen@maastrichtuniversity.nl}   % email address
]{\inits{ELW}\fnm{Egon L} \snm{Willighagen}}
\author[
   addressref={aff2},
   email={john@nextmovesoftware.com}
]{\inits{JWM}\fnm{John W} \snm{May}}
\author[
   addressref={uppsala},
   email={jonathan.alvarsson@farmbio.uu.se}
]{\inits{JA}\fnm{Jonathan} \snm{Alvarsson}}
\author[
   addressref={uppsala},
   email={berg.arvid@gmail.com}
]{\inits{AB}\fnm{Arvid} \snm{Berg}}
\author[
   addressref={jena},
   email={kai.duehrkop@uni-jena.de}
]{\inits{KD}\fnm{Kai} \snm{Dührkop}}
\author[
   addressref={idea},
   email={jeliazkova.nina@gmail.com}
]{\inits{NJ}\fnm{Nina} \snm{Jeliazkova}}
\author[
   addressref={leicester},
   email={shk12@le.ac.uk}
]{\inits{SK}\fnm{Stefan} \snm{Kuhn}}
\author[
   addressref={wi_mit},
   email={pluskal@wi.mit.edu}
]{\inits{TP}\fnm{Tomáš}~\snm{Pluskal}}
\author[
   addressref={miquel},
   email={miguelrojasch@googlemail.com}
]{\inits{MRJ}\fnm{Miquel}~\snm{Rojas Chertó}}
\author[
   addressref={uppsala},
   email={ola.spjuth@farmbio.uu.se}
]{\inits{OS}\fnm{Ola} \snm{Spjuth}}
\author[
   addressref={gilleain},                           % ORCID: 0000-0002-8368-6954
   email={gilleain.torrance@gmail.com}
]{\inits{GT}\fnm{Gilleain} \snm{Torrance}}
\author[
   addressref={um},
   email={chris.evelo@maastrichtuniversity.nl}
]{\inits{CTE}\fnm{Chris T} \snm{Evelo}}
\author[
   addressref={nih},
   email={guhar@mail.nih.gov}
]{\inits{RG}\fnm{Rajarshi} \snm{Guha}}
\author[
   addressref={ebi},
   email={steinbeck@ebi.ac.uk}
]{\inits{CS}\fnm{Christoph}~\snm{Steinbeck}}

\address[id=um]{
  \orgname{Dept of Bioinformatics - BiGCaT, NUTRIM, Maastricht University}, % university, etc
  %\street{Waterloo Road},
  \postcode{NL-6200 MD},
  \city{Maastricht},
  \cny{The Netherlands}
}
\address[id=aff2]{
  %\orgname{??},
  %\street{D\"{u}sternbrooker Weg 20},
  %\postcode{24105},
  %\city{Kiel},
  \cny{UK}
}
\address[id=uppsala]{
  \orgname{Department of Pharmaceutical Biosciences, Uppsala University},
  %\street{D\"{u}sternbrooker Weg 20},
  \postcode{751 24},
  \city{Uppsala},
  \cny{Sweden}
}
\address[id=jena]{
  \orgname{Chair for Bioinformatics, Friedrich Schiller University},
  %\street{},
  \postcode{07743},
  \city{Jena},
  \cny{Germany}
}
\address[id=idea]{
  \orgname{Ideaconsult Ltd},
  \street{A. Kanchev 4},
  \postcode{1000},
  \city{Sofia},
  \cny{Bulgaria}
}
\address[id=wi_mit]{
  \orgname{Whitehead Institute for Biomedical Research}, 
  \street{9 Cambridge Center},
  \postcode{MA 02142},
  \city{Cambridge},
  \cny{USA}
}
\address[id=miquel]{
  %\orgname{Department of Informatics, University of Leicester},
  %\street{4 Hanway Place},
  %\postcode{W1T 1HD},
  %\city{London},
  \cny{Spain}
}
\address[id=gilleain]{
  %\orgname{Department of Informatics, University of Leicester},
  \street{4 Hanway Place},
  \postcode{W1T 1HD},
  \city{London},
  \cny{UK}
}
\address[id=nih]{
  \orgname{National Center for Advancing Translational Science},
  \street{9800 Medical Center Drive},
  \postcode{MD 20878},
  \city{Rockville},
  \cny{USA}
}
\address[id=ebi]{
  \orgname{Chemoinformatics and Metabolism team, European Bioinformatics Institute},
  %\street{A. Kanchev 4},
  %\postcode{1000},
  \city{Hinxton},
  \cny{UK}
}
\address[id=leicester]{
  \orgname{Department of Informatics, University of Leicester},
  %\street{},
  %\postcode{LE1 7RH},
  \city{Leicester},
  \cny{UK}
}
